### 2018-10-05 paper/paper.tex
proof lemma

The higher the standard deviation of the demand, the more likely it is to find high fluctuations in
the release pattern. Thus, the scaled deviations in the demand specify a natural lower-bound of
release decisions to consider in the analysis of the \LTS{}.
%
Hence, we use the standard deviation $\sigma$ of the random variable $\X$ in relation to the mean
demand as measure for determining the time span being considered. Recall that the standard deviation
measures the expected deviation of the mean in orders.
%
%
% Thus, $2 \sigma$ specify the (minimum) expected deviation of the demand and thus also the release
% decisions from one period to the next.
%
Futhermore,... \MS[t]{seasonal stuff}
%

>>>>

\begin{lemma}

  % stddev(rel1) > stddev(rel0) -> stddev(dem1) > stddev(dem0)
  It is sensible to increase the standard deviation in the release pattern if the standard deviation
  in the demand increases.

\end{lemma}

\begin{proof}{Proof by induction on the size of the deviations.}
  Wlog assume sufficient capacity for the single-stage manufacturer.
  % Base: stddev(rel1) > 0 -> stddev(dem1) > 0
  In case of a constant
  demand pattern, the only sensible release pattern is to release s.t. an over the time (nearly)
  constant output in the magnitude of the demand is achieved.
  % or the maximum achievable constant throughput.
  Any other release pattern will increase either back-orders or finished goods inventory and thus
  costs. Similarly the costs increase once variability in the demand is introduced, as possible
  unforeseen fluctuations in the demand require either to increase the stock level or accept
  back-order costs.
  %
  % IH: stddev(dem1) > stddev(dem0) -> stddev(rel1) > stddev(rel0)
  In case the demand deviation increases by any magnitude greater $0$, chances for the demand
  quantities further away from the mean are increased with probability $p>0$. Thus the planner has
  to decide whether to release additional quantity to be able to serve the demand which is more
  likely with probability $p$. Clearly, this increases chances for either inventory costs or
  back-order costs according to the decision of the planner and compared to the previous situation.
  \qed

  % Demand with higher stddev
  % ----
  % ---
  % --
  % ---
  % ----

  % Demand with lower stddev
  % ---
  % ---
  % ---
  % ---
  % ---

\end{proof}

Put differently, for higher standard deviation in the demand higher fluctuations in the release
pattern are sensible. Thus, the scaled deviations in the demand specify a natural lower-bound of
release decisions to consider in the analysis of the \LTS{}.
%
Hence, we use the standard deviation $\sigma$ of the random variable $\X$ in relation to the mean
demand as measure for determining the time span of the release decisions and \WIP{}-levels being
considered in the analysis. Recall that the standard deviation measures the expected deviation of
the mean in orders.
%
%
% Thus, $2 \sigma$ specify the (minimum) expected deviation of the demand and thus also the release
% decisions from one period to the next.
%
Futhermore,... \MS[t]{seasonal stuff}
%
